Approximation as Differentiation notes

### 2025-02-10 notes.tex
Force to A4.
Ok, think I see how Fam(C) is a Grothendieck construction.

@@

\settopmatter{printacmref=false}

@@

\noindent Equivalently $\Fam(I,C)$ is the functor category $\FunCat{I}{C}$ where we interpret $I$ as a
discrete category.

@@

\noindent This is the Grothendieck construction for a functor $F: C \to \Cat$, in the special case where $F: C
\to \Set$ (where we read a $\Set$-valued functor as a $\Cat$-valued functor restricted to discrete
categories).

In our code we give a slightly different construction, namely the fibred category $\Fam(C)$ over $\Set$ where:
\begin{itemize}
\item objects are pairs $(I, X)$ of a set $I$ and indexed family $X$ in $\Fam(I,C)$;
\item morphisms from $(I, X)$ to $(J, Y)$ are functions $f: I \to J$ paired with morphisms $X \to Y[f]$ in
$\Fam(I,C)$.
\end{itemize}

@@

We interpret our language into any category with:
\begin{itemize}
\item finite products (binary products and a terminal object)
\item Booleans
\end{itemize}
\note{Ignoring lists for now; Booleans can be derived from coproducts.}

>>>>

\geometry{paperwidth=8.3in, paperheight=11.7in} % force to A4 for now
\settopmatter{printacmref=false}

@@

@@

\noindent Equivalently $\Fam(I,C)$ is the functor category $\Func{I}{C}$ where we interpret $I$ as a discrete
category.

@@

\noindent This is the Grothendieck construction for a functor $F: C \to \Cat$ for the special case where $F: C
\to \Set$ (where we read a $\Set$-valued functor as a $\Cat$-valued functor restricted to discrete
categories).

Define the fibred category $\Fam(C)$ over $\Set$ where:
\begin{itemize}
\item objects are pairs $(I, X)$ of a set $I$ and indexed family $X$ in $\Fam(I,C)$;
\item morphisms from $(I, X)$ to $(J, Y)$ are functions $f: I \to J$ paired with morphisms $X \to Y[f]$ in
$\Fam(I,C)$.
\end{itemize}

\noindent This is the Grothendieck construction for the functor $\Set^{\op} \to \Cat$ which sends any set $I$
to the category $\Fam(I,C)$ and any function $f: I \to J$ to the reindexing functor $-[f]: \Fam(J,C) \to
\Fam(I,C)$.

@@

We interpret our language into any category with:
\begin{itemize}
\item finite products (binary products and a terminal object)
\item Booleans
\end{itemize}
\note{Ignoring lists for now. Booleans can be derived from coproducts.}
